---
title: "Group_06_Analysis"
author: "Hao Wu,Yiliang Shen,Jingting Zhao,Jinshen Zhang,Ninad Khare"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE, comment = NA)
```

```{r libraries}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(moderndive)
library(gapminder)
library(sjPlot)
library(stats)
library(jtools)
library(kableExtra)
library(gridExtra)
library(skimr)
library(GGally)
library(readr)
```

# Introduction {#sec:intro}

The IMDB film database contains a collection of seven characteristics about the films such as year of showing, length of film, production budget and the rating and others.

We are interested in which properties of films influence whether they are rated by IMDB as greater than 7 or not.

```{r data, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}

#Data pre-processing

#Set the current working directory
setwd("/我的桌面")

#Read data and Remove invalid data rows with null values
film<-na.omit(read.csv("dataset6.csv"))

#add new variables according to whether the rating which takes the value 1 if rating is greater than 7, otherwise 0
film<-film%>%
  mutate(rate_value=ifelse(rating> 7,1,0))%>%
  mutate(rate=ifelse(rating> 7,'Greater than 7','Less than 7'))
#the data we want to use to explore the question
film_data<-film%>%
  select(Year=year,
         Length=length,
         Budget=budget,
         Genre=genre,
         Rate=rate,
         Rate_value=rate_value)
```

# Exploratory data analysis {#sec:eda}

## Variable Description

The following is the explanatory variables and the response variable we are interested in.

***Year***: Year of release of the film in cinemas.

***Length***: Duration (in minutes).

***Budget***: Budget for the films production (in \$1000000s).

***Genre***: Genre of the film.

***Rate***: Whether the rating of the film is greater than 7.

***Rate_value***: If the rate of the film is greater than 7, takes the value 1.Otherwise, takes the value 0.

The following table shows the dataset which contains all the variables we are interested in.

```{r, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}
#Data table display after data cleaning
kable(head(film_data, n = 5), caption = '\\label{tab:filmdata} The first 5 rows of the film data',align = "c") %>% 
  kable_styling(full_width = F)%>% 
  column_spec(1, bold = T)%>%
  kable_styling(font_size = 10, latex_options = 'h')
```

## Data visualization display

The Box Plot can first be used to make a comparison of the characteristics of the distribution of multiple sets of data. The graph below explains well the distribution of the three continuous variables (Year,Length,Budget) on whether the movie rating is greater than 7.

```{r, eval = TRUE,  out.width = '75%', fig.align = "center", warning = FALSE, fig.pos="H",fig.cap = '\\label{fig:rate} Continous Variables VS Rate.'}
p1<-ggplot(data = film_data, aes(x = Rate, y = Year, fill = Rate)) +
  geom_boxplot() +
  labs(x = "Rate", y = "Year")+ 
  theme(legend.position = "none")
p2<-ggplot(data = film_data, aes(x = Rate, y = Length, fill = Rate)) +
  geom_boxplot() +
  labs(x = "Rate", y = "Length")+ 
  theme(legend.position = "none")
p3<-ggplot(data = film_data, aes(x = Rate, y = Budget, fill = Rate)) +
  geom_boxplot() +
  labs(x = "Rate", y = "Budget")+ 
  theme(legend.position = "none")
grid.arrange(p1,p2,p3,nrow=2)
```

## Correlation matrix

Before we use these continuous variables to fit the Generalized Linear Model(GLM), check the correlation between different variables first.

```{r, eval = TRUE, out.width = '80%', fig.align = "center",warning = FALSE, fig.pos="H",fig.cap = '\\label{fig:gini} The correlation coefficient between variables.'}
#Obtain the correlation coefficient between variables
ggpairs(film[c("year","length","budget")])
```

As the plot shown above, the correlation between different variables are quite low.

The following plot implies that the categorical variable ***Genre*** is useful for the prediction of the response variable ***Rate_value***.

It can be seen that the two bar charts on the left and right are almost perfectly complementary, with the Romance genre scoring a relatively low percentage of films with rating greater than seven.

```{r, eval = TRUE,  out.width = '80%', fig.align = "center", warning = FALSE,  fig.pos="H",fig.cap = '\\label{fig:rate} Proportion of different genres of each Rate.'}
ggplot(film, aes(x= rate,  y = ..prop.., group=genre, fill=genre)) + 
    geom_bar(position="dodge", stat="count") +
    labs(y = "Proportion")
```

# Formal analysis with Generalised Linear Model

## The model fitted

The model we fitted is the following: \begin{align}
\ln\left(\frac{p}{1-p}\right) &= \alpha + \beta_1 \cdot \textrm{Year}+\beta_2 \cdot \textrm{Length}+\beta_3 \cdot \textrm{Budget}+\beta_4 \cdot I_{Animation}+\beta_5 \cdot I_{Comedy} +\nonumber \\
&\beta_6 \cdot I_{Documentary}+\beta_7 \cdot I_{Drama}+\beta_8 \cdot I_{Romance}+\beta_9 \cdot I_{Short} 
\end{align} where $p\ =$ Prob(Rate greater than 7) and $1-p\ =$ Prob(Rate less than 7) and the fitted result shows in the following:

```{r data2, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}
model.film <- glm(Rate_value~Year+Length+Budget+Genre, data = film_data,
                  family = binomial(link = "logit"))
model.film%>%
  summary()
```

Hence, from the result we got, we have known the values of $\alpha$ and $\beta_{i}$, such as $\beta_1 \ =\ 0.010194$, which means the log-odds of the rate of the film being greater than 7 increase by 0.010194 for every one unit increase in Year.

## Confidence interval

Comparing to the point estimates of the influence of the variables, the following shows the 95% confidence intervals, figure and the estimates for these log-odds:

```{r, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}
confint(model.film) %>%
  kable(caption = '\\label{tab:filmdata} Confidence Interval',align = "c") %>% 
  kable_styling(full_width = F)%>% 
  column_spec(1, bold = T)%>%
  kable_styling(font_size = 10, latex_options = 'h')
```

```{r, eval = TRUE,  out.width = '80%', fig.align = "center", warning = FALSE,  fig.pos="H",fig.cap = '\\label{fig:rate} The log-odds for different variables.'}
plot_model(model.film, show.values = TRUE, transform = NULL,
           title = "Log-Odds (Film rate greater than 7)", show.p = FALSE)
```
The 95% confidence interval for the different variables can be observed more visualized in the picture in the area around zero.To be specific, if the log odds are positive but close to zero, then it is slightly more likely to win than to lose. If the log odds are negative but close to zero, then the chances of losing are marginally greater than the chances of winning.

Moreover, the larger the absolute value of the log odds, the less likely the bet is to succeed. So for the movie dataset used, the larger the absolute value of the log odds, the less likelihood of a rating greater than 7.

The following table contains the log-odds within the dataset. The following table lists the first 5 rows of the film data with logodds.

```{r, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}

film_data<-film_data%>%
  mutate(logodds.Greater_than_7 = predict(model.film))
kable(head(film_data, n = 5), caption = '\\label{tab:filmdata} The first 5 rows of the film data with logodds',align = "c") %>% 
  kable_styling(full_width = F)%>% 
  
  kable_styling(font_size = 10, latex_options = 'h')
```


Instead of the log-odds, the following shows the figure and the estimates of the odds, which is: \begin{align}
\frac{p}{1-p}\ &= exp(\alpha+ \beta_1 \cdot \textrm{Year}+\beta_2 \cdot \textrm{Length}+\beta_3 \cdot \textrm{Budget}+\beta_4 \cdot I_{Animation}+\beta_5 \cdot I_{Comedy} +\nonumber \\
&\beta_6 \cdot I_{Documentary}+\beta_7 \cdot I_{Drama}+\beta_8 \cdot I_{Romance}+\beta_9 \cdot I_{Short})
\end{align}

```{r, eval = TRUE,  out.width = '80%', fig.align = "center", warning = FALSE,  fig.pos="H",fig.cap = '\\label{fig:rate} The odds for different variables.'}
plot_model(model.film, show.values = TRUE, axis.lim = c(0.001,40),
           title = "Odds (Film rate greater than 7)", show.p = FALSE)

```


```{r, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}

film_data<-film_data%>%
  mutate(odds.Greater_than_7 = exp(logodds.Greater_than_7))
kable(head(film_data, n = 5), caption = '\\label{tab:filmdata} The first 5 rows of the film data with odds',align = "c") %>%  
  column_spec(c(2,3), width = "21px") %>%
  kable_styling(font_size = 8, latex_options = 'h')
```

## Probability

We can obtain the probability $p\ =$ Prob(Rate greater than 7) using the Formula (2) above using the transformation: $p\ =\frac{(2)}{1+(2)}$

```{r, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}

film_data<-film_data%>%
  mutate(p=fitted(model.film))
kable(head(film_data, n = 5), caption = '\\label{tab:filmdata} The first 5 rows of the film data with p',align = "c")%>%
  kable_styling(font_size = 7, latex_options = 'h')%>%
  column_spec(c(2,3), width = "19px") %>%
  column_spec(4, width = "40px") %>%
  column_spec(6, width = "36px") %>%
  column_spec(8, width = "72px") 
```

In order to observe the effectiveness of the model fit then, plots are drawn for comparing the predicted and observed values.

The 95% confidence interval of the prediction is shaded, and the wider the confidence interval, the wider the shaded part. Consequently, the width of the shaded portion in the plot of predicted versus observed values gives a clearer understanding of the uncertainty in the predicted results.

The fitted out regression line gives a straightforward way to describe the overall trend of the model and how well the model fits. This line is supposed to offer a good match to the data points in the scatter plot.

As can be seen in the three cases of continuous type variables (Figures 6-8), the shaded part of the picture is moderately wide and the fitting line falls within the shaded part, which demonstrates that this model is very effective.

The figures of the Prob. of each explanatory variables using the fitted model show below:

```{r, eval = TRUE,  out.width = '80%', fig.align = "center", warning = FALSE,  fig.pos="H",fig.cap = '\\label{fig:rate} Comparing predictions and observations.'}

plot_model(model.film,type = "pred",title = "Prob. of the rate of the film greater than 7")
```
