---
title: "Group_06_Analysis"
author: "Hao Wu,Yiliang Shen,Jingting Zhao,Jinshen Zhang,Ninad Khare"
output:
  html_document:
    df_print: paged
  github_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE, comment = NA)
```

```{r libraries}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(moderndive)
library(gapminder)
library(sjPlot)
library(stats)
library(jtools)
library(kableExtra)
library(gridExtra)
library(skimr)
library(GGally)
library(readr)
```

# Introduction {#sec:intro}

We are interested in which properties of films influence whether they are rated by IMDB as greater than 7 or not.

```{r data, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}

#Data pre-processing

#Set the current working directory
#setwd("/Users/jason/Desktop")

#Read data and Remove invalid data rows with null values
film<-na.omit(read.csv("dataset6.csv"))

#add new variables according to whether the rating which takes the value 1 if rating is greater than 7, otherwise 0
film<-film%>%
  mutate(rate_value=ifelse(rating> 7,1,0))%>%
  mutate(rate=ifelse(rating> 7,'Greater than 7','Less than 7'))
#the data we want to use to explore the question
film_data<-film%>%
  select(Year=year,
         Length=length,
         Budget=budget,
         Genre=genre,
         Rate=rate,
         Rate_value=rate_value)
```

# Exploratory data analysis {#sec:eda}

## Variable Description

The following is the explanatory variables and the response variable we are interested in.

***Year***: Year of release of the film in cinemas.

***Length***: Duration (in minutes).

***Budget***: Budget for the films production (in \$1000000s).

***Genre***: Genre of the film.

***Rate***: Whether the rating of the film is greater than 7.

***Rate_value***: If the rate of the film is greater than 7, takes the value 1.Otherwise, takes the value 0.

The following table shows the dataset which contains all the variables we are interested in.

```{r, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}
#Data table display after data cleaning
kable(head(film_data, n = 5), caption = '\\label{tab:filmdata} The first 5 rows of the film data')%>%
  kable_styling(font_size = 10, latex_options = 'h')
```

## Data visualization display

```{r, eval = TRUE,  out.width = '100%', fig.align = "center", warning = FALSE, fig.cap = '\\label{fig:rate} Continous Variables VS Rate.'}
p1<-ggplot(data = film_data, aes(x = Rate, y = Year, fill = Rate)) +
  geom_boxplot() +
  labs(x = "Rate", y = "Year")+ 
  theme(legend.position = "none")
p2<-ggplot(data = film_data, aes(x = Rate, y = Length, fill = Rate)) +
  geom_boxplot() +
  labs(x = "Rate", y = "Length")+ 
  theme(legend.position = "none")
p3<-ggplot(data = film_data, aes(x = Rate, y = Budget, fill = Rate)) +
  geom_boxplot() +
  labs(x = "Rate", y = "Budget")+ 
  theme(legend.position = "none")
grid.arrange(p1,p2,p3,nrow=2)
```

## correlation matrix

Before we use these continous variables to fit the Generalised Linear Model(GLM), check the correlation between different variables first.

```{r, eval = TRUE, out.width = '80%', fig.align = "center",warning = FALSE, fig.cap = '\\label{fig:gini} The correlation coefficient between variables.'}
#Obtain the correlation coefficient between variables
ggpairs(film[c("year","length","budget")])
```

As the plot shown above, the correlation between different variables are quite low.

The following plot implies that the categorical variable ***Genre*** is useful for the prediction of the response variable ***Rate_value***

```{r, eval = TRUE,  out.width = '80%', fig.align = "center", warning = FALSE, fig.cap = '\\label{fig:rate} Proportion of different genres of each Rate.'}
ggplot(film, aes(x= rate,  y = ..prop.., group=genre, fill=genre)) + 
    geom_bar(position="dodge", stat="count") +
    labs(y = "Proportion")
```

# Formal analysis with Generalised Linear Model

## The model fitted

The model we fitted is the following: \begin{align}
\ln\left(\frac{p}{1-p}\right) &= \alpha + \beta_1 \cdot \textrm{Year}+\beta_2 \cdot \textrm{Length}+\beta_3 \cdot \textrm{Budget}+\beta_4 \cdot I_{Animation}+\beta_5 \cdot I_{Comedy} +\nonumber \\
&\beta_6 \cdot I_{Documentary}+\beta_7 \cdot I_{Drama}+\beta_8 \cdot I_{Romance}+\beta_9 \cdot I_{Short} 
\end{align} where $p\ =$ Prob(Rate greater than 7) and $1-p\ =$ Prob(Rate less than 7) and the fitted result shows in the following:

```{r data2, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}
model.film <- glm(Rate_value~Year+Length+Budget+Genre, data = film_data,
                  family = binomial(link = "logit"))
model.film%>%
  summary()
```

Hence, from the result we got, we have known the values of $\alpha$ and $\beta_{i}$, such as $\beta_1 \ =\ 0.010194$, which means the log-odds of the rate of the film being greater than 7 increase by 0.010194 for every one unit increase in Year.

## Confidence interval

Comparing to the point estimates of the influence of the variables, the following shows the 95% confidence intervals, figure and the estimates for these log-odds:

```{r, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}
confint(model.film) %>%
  kable(caption = '\\label{tab:filmdata} Confidence Interval')%>%
  kable_styling(font_size = 10, latex_options = 'h')
```

```{r, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}
plot_model(model.film, show.values = TRUE, transform = NULL,
           title = "Log-Odds (Film rate greater than 7)", show.p = FALSE)
film_data<-film_data%>%
  mutate(logodds.Greater_than_7 = predict(model.film))
kable(head(film_data, n = 5), caption = '\\label{tab:filmdata} The first 5 rows of the film data with logodds')%>%
  kable_styling(font_size = 10, latex_options = 'h')
```

We simply exponentiate the log-odds to get odds, the following shows the figure and the estimates of the odds, which is:
$$
\begin{align}
\frac{p}{1-p}\ &= exp(\alpha+ \beta_1 \cdot \textrm{Year}+\beta_2 \cdot \textrm{Length}+\beta_3 \cdot \textrm{Budget}+\beta_4 \cdot I_{Animation}+\beta_5 \cdot I_{Comedy} +\nonumber \\
&\beta_6 \cdot I_{Documentary}+\beta_7 \cdot I_{Drama}+\beta_8 \cdot I_{Romance}+\beta_9 \cdot I_{Short})
\end{align}
$$

```{r exp_log_odds, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}
# exponentiate the log-odds
model.film %>%
  coef() %>%
  exp()
```

For $Year$ we have an odds of $1.01$, which indicates that for every 1 unit increase in $Year$, the odds of the film with rating greater than 7 increase by a factor of 1.01. And the rest coefficients of variables perform the same thing. Odds-ratio obtained from year 2000 and 2001 can be calculated as the following:
$$
\begin{align}
\frac{Odds_{Year=2001}}{Odds_{Year=2000}}&=
\frac{\frac{p_{Year=2001}}{1-p_{Year=2001}}}{\frac{p_{Year=2000}}{1-p_{Year=2000}}}\\
&=\frac{exp(\alpha+\beta_1\cdot2001+K)}
{exp(\alpha+\beta_1\cdot2000+K)}\\
&=exp(\beta_1 \cdot(2001-2000))\\
&=exp(0.010194)\\
&=1.01\\
\text{ where K} &=\beta_2\cdot\textrm{Length}+\beta_3\cdot\textrm{Budget}
+\beta_4\cdot I_{Animation}+\beta_5\cdot I_{Comedy}\\&+\beta_6\cdot I_{Documentary}+
\beta_7\cdot I_{Drama}+\beta_8\cdot I_{Romance}+\beta_9\cdot I_{Short})\\
\end{align}
$$

```{r, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}
plot_model(model.film, show.values = TRUE, axis.lim = c(0.001,40),
           title = "Odds (Film rate greater than 7)", show.p = FALSE)
film_data<-film_data%>%
  mutate(odds.Greater_than_7 = exp(logodds.Greater_than_7))
kable(head(film_data, n = 5), caption = '\\label{tab:filmdata} The first 5 rows of the film data with odds')%>%
  kable_styling(font_size = 8, latex_options = 'h')
```

## Probability

We can obtain the probability $p\ =$ Prob(Rate greater than 7) using the Formula (2) above using the transformation: $p\ =\frac{(2)}{1+(2)}$

```{r, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}
film_data<-film_data%>%
  mutate(p=fitted(model.film))
kable(head(film_data, n = 5), caption = '\\label{tab:filmdata} The first 5 rows of the film data with p')%>%
  kable_styling(font_size = 7, latex_options = 'h')
```

The figures of the Prob. of each explanatory variables using the fitted model show below:

```{r, echo = FALSE, eval = TRUE,out.width = '90%', fig.align = "center", warning = FALSE, message = FALSE}
plot_model(model.film,type = "pred",title="Prob. of the rate of the film greater than 7")
```
