---
title: "Group_06_Analysis"
author: "Hao Wu,Yiliang Shen,Jingting Zhao,Jinshen Zhang,Ninad Khare"
output:
  pdf_document: default
  github_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE, comment = NA)
```

```{r libraries}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(moderndive)
library(gapminder)
library(sjPlot)
library(stats)
library(jtools)
library(kableExtra)
library(gridExtra)
library(skimr)
library(GGally)
library(readr)
```

# Introduction {#sec:intro}

The IMDB film database contains a collection of seven characteristics about the films such as year of showing, length of film, production budget and the rating and others.

We are interested in which properties of films influence whether they are rated by IMDB as greater than 7 or not.

```{r data, echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}

#Data pre-processing
#Set the current working directory

setwd("/Users/jason/Desktop")

#Read data and Remove invalid data rows with null values
film<-na.omit(read.csv("dataset6.csv"))
#add new variables according to whether the rating is greater than 7
film<-film%>%
  mutate(rate_value=ifelse(rating> 7,1,0))%>%
  mutate(rate=ifelse(rating> 7,'Greater than 7','Less than 7'))
#the data we want to use to explore the question
film_data<-film%>%
  select(Year=year,
         Length=length,
         Budget=budget,
         Genre=genre,
         Rate=rate,
         Rate_value=rate_value)
```

# Exploratory data analysis {#sec:eda}

## Variable Description

The following is the explanatory variables and the response variable we are interested in.

**Year**: Year of release of the film in cinemas.

**Length**: Duration (in minutes).

**Budget**: Budget for the films production (in \$1000000s).

**Genre**: Genre of the film.

**Rate**: Whether the rating of the film is greater than 7.

**Rate_value**: If the rate of the film is greater than 7, takes the value 1.Otherwise, takes the value 0.

The following table shows the first 5 rows of the dataset which contains all the variables we are interested in.

```{r, echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}
#Data table display after data process
kable(head(film_data, n = 5), 
      caption = '\\label{tab:filmdata} The first 5 rows of the film data',
      align = "c") %>% 
kable_styling(full_width = F,font_size = 10, latex_options = 'h')
```

## Data visualization display


### Boxplots
The Boxplot can first be used to compare the characteristics of the distribution of multiple sets of data. The graph below explains well the distribution of the three continuous variables (Year, Length, Budget) on whether the movie rating is greater than 7. 

```{r, echo = TRUE ,eval = TRUE,  out.width = '75%', fig.align = "center", warning = FALSE, fig.pos="H",fig.cap = '\\label{fig:rate} Boxplot of Continous Variables VS Rate.'}

#get Boxplot
p1<-ggplot(data = film_data, aes(x = Rate, y = Year, fill = Rate)) +
  geom_boxplot() +
  labs(x = "Rate", y = "Year")+ 
  theme(legend.position = "none")
p2<-ggplot(data = film_data, aes(x = Rate, y = Length, fill = Rate)) +
  geom_boxplot() +
  labs(x = "Rate", y = "Length")+ 
  theme(legend.position = "none")
p3<-ggplot(data = film_data, aes(x = Rate, y = Budget, fill = Rate)) +
  geom_boxplot() +
  labs(x = "Rate", y = "Budget")+ 
  theme(legend.position = "none")
grid.arrange(p1,p2,p3,nrow=2)
```


The distribution of the variables **Year** and **Budget** are symmetric in each of the two categories. Films with rating greater than 7 are higher in more modern publishing years and have higher budget. However, the distribution of the **Length** of the films between the two categories has a significant difference, which can be seen the length of the films with the rate less than 7 is more likely longer than those with the rate greater than 7 and has a minor variance.


### Correlation matrix


Before we use these continuous variables to fit the Generalized Linear Model(GLM), check the correlation between different variables first.

```{r,echo = TRUE, eval = TRUE, out.width = '60%', fig.align = "center",warning = FALSE, fig.pos="H",fig.cap = '\\label{fig:gini} The correlation coefficient between continous variables.'}
#Obtain the correlation coefficient between continuous variables
ggpairs(film_data[c("Year","Length","Budget")])
```

As the figure shown above, the correlation between different variables are quite low, which means it is reasonable to select all of them to fit the model.


### Histogram for Genre
The following plot implies that the categorical variable **Genre** is useful for the prediction of the response variable **Rate_value**.

It can be seen that the two bar charts on the left and right are almost perfectly complementary, with the Romance genre scoring a relatively low percentage of films with rating greater than seven.

```{r,echo = TRUE, eval = TRUE,  out.width = '60%', fig.align = "center", warning = FALSE,  fig.pos="H",fig.cap = '\\label{fig:rate} Proportion of different genres of Rate.'}
#get the histogram of the proportion in each category
ggplot(film_data, aes(x= Rate,  y = ..prop.., group=Genre, fill=Genre)) + 
    geom_bar(position="dodge", stat="count") +
    labs(y = "Proportion")
```

# Formal analysis with Generalised Linear Model

## The model fitted

The model we fitted is the following: \begin{align}
\ln\left(\frac{p}{1-p}\right) &= \alpha + \beta_1 \cdot \textrm{Year}+\beta_2 \cdot \textrm{Length}+\beta_3 \cdot \textrm{Budget}+\beta_4 \cdot I_{Animation}+\beta_5 \cdot I_{Comedy} +\nonumber \\
&\beta_6 \cdot I_{Documentary}+\beta_7 \cdot I_{Drama}+\beta_8 \cdot I_{Romance}+\beta_9 \cdot I_{Short} 
\end{align} where $p\ =$ Prob(Rate greater than 7) and $1-p\ =$ Prob(Rate less than 7) and the fitted result shows in the following:

```{r ,echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}

#fit the GLM 
model.film <- glm(Rate_value~Year+Length+Budget+Genre, data = film_data,
                  family = binomial(link = "logit"))
model.film%>%
  summary()
```

Hence, from the result we got, we have known the values of $\alpha$ and $\beta_{i}$, such as $\beta_1 \ =\ 0.010194$, which means the log-odds of the rate of the film being greater than 7 increase by 0.010194 for every one unit increase in **Year**.

## Confidence interval

Comparing to the point estimates of the influence of the variables, the following shows the 95% confidence intervals, figure and the estimates for these log-odds:


```{r,echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}
#calculate CI for log-odds of each variable
confint(model.film) %>%
  kable(caption = '\\label{tab:filmdata} Confidence Interval',align = "c") %>% 
  column_spec(1, bold = T)%>%
  kable_styling(full_width = F,font_size = 10, latex_options = 'h')
```


```{r,echo = TRUE, eval = TRUE,  out.width = '80%', fig.align = "center", warning = FALSE,  fig.pos="H",fig.cap = '\\label{figrate} The log-odds for different variables.'}

#Show CI in plot
plot_model(model.film, show.values = TRUE, transform = NULL,
           title = "Log-Odds (Film rate greater than 7)", show.p = FALSE)
```
The 95% confidence interval for the different variables can be observed more visualized in the Figure 4.

The following table shows the first 5 rows of the estimates of the log-odds given by the fitted model. 

```{r,echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}
#get the estimates of log-odds
film_data<-film_data%>%
  mutate(logodds.Greater_than_7 = predict(model.film))
kable(head(film_data, n = 5),
      caption = '\\label{tab:filmdata} The first 5 rows of the film data with log-odds',
      align = "c") %>%
  column_spec(7, bold = T)%>%
  kable_styling(full_width = F,font_size = 10, latex_options = 'h')
```


To be specific, if the log-odds is positive, then the random experiment is more likely to succeed than to lose. In contrast, if the log-odds is negative, then the probability of losing is greater than success. 

Moreover, the larger the absolute value of the log-odds, the greater the difference in the probability of success and failure of a trial. As for the question we are interested in, the larger the absolute value of the negative log-odds, the less likelihood of the movie rates greater than 7.


Instead of the log-odds, the following shows the figure and the estimates of the odds, which is: 

\begin{align}
\frac{p}{1-p}\ &= exp(\alpha+ \beta_1 \cdot \textrm{Year}+\beta_2 \cdot \textrm{Length}+\beta_3 \cdot \textrm{Budget}+\beta_4 \cdot I_{Animation}+\beta_5 \cdot I_{Comedy} +\nonumber \\
&\beta_6 \cdot I_{Documentary}+\beta_7 \cdot I_{Drama}+\beta_8 \cdot I_{Romance}+\beta_9 \cdot I_{Short})
\end{align}

We simply exponentiate the log-odds to get odds, the following shows the figure and the estimates of the odds, which is:
```{r exp_log_odds, echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}
# exponentiate the log-odds
model.film %>%
  coef() %>%
  exp()
```

For **Year** we have an odds of **1.01**, which indicates that for every 1 unit increase in **Year**, the odds of the film with rating greater than 7 increase by a factor of 1.01. And the rest coefficients of variables perform the same thing. Odds-ratio obtained from year 2000 and 2001 can be calculated as the following:

\begin{align}
\frac{Odds_{Year=2001}}{Odds_{Year=2000}}&=
\frac{\frac{p_{Year=2001}}{1-p_{Year=2001}}}{\frac{p_{Year=2000}}{1-p_{Year=2000}}}
\nonumber \\
&=\frac{exp(\alpha+\beta_1\cdot2001+K)}
{exp(\alpha+\beta_1\cdot2000+K)}\nonumber \\
&=exp(\beta_1 \cdot(2001-2000))\nonumber \\
&=exp(0.010194)\nonumber \\
&=1.01\nonumber \\
\text{ where K} &=\beta_2\cdot\textrm{Length}+\beta_3\cdot\textrm{Budget}
+\beta_4\cdot I_{Animation}+\beta_5\cdot I_{Comedy}\nonumber \\
&+\beta_6\cdot I_{Documentary}+\beta_7\cdot I_{Drama}+\beta_8\cdot I_{Romance}+\beta_9\cdot I_{Short}) \nonumber
\end{align}


As shown above, we can obtain the 95% confidence intervals of the odds by simply exponentiation the lower and upper bounds of our log-odds intervals, the following shows the figure of the confidence intervals and the estimates of the odds:

```{r,echo = TRUE, eval = TRUE,  out.width = '80%', fig.align = "center", warning = FALSE,  fig.pos="H",fig.cap = '\\label{fig:rate} The odds for different variables.'}

#Show CI for odds in plot
plot_model(model.film, show.values = TRUE, axis.lim = c(0.001,40),
           title = "Odds (Film rate greater than 7)", show.p = FALSE)

```

```{r, echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}
#the estimates of the odds
film_data<-film_data%>%
  mutate(odds.Greater_than_7 = exp(logodds.Greater_than_7))
kable(head(film_data, n = 5), 
      caption = '\\label{tab:filmdata} The first 5 rows of the film data with odds',
      align = "c") %>%  
  column_spec(8, bold = T) %>%
  column_spec(c(2,3), width = "21px")%>%
  kable_styling(font_size = 8, latex_options = 'h')
```


## Probability

We can obtain the probability $p\ =$ Prob(Rate greater than 7) using the Formula (2) above using the transformation: $p\ =\frac{(2)}{1+(2)}$


```{r, echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}

#Add probability to original dataset
film_data<-film_data%>%
  mutate(p=fitted(model.film))
kable(head(film_data, n = 5),
      caption = '\\label{tab:filmdata} The first 5 rows of the film data with p',
      align = "c")%>%
  column_spec(9, bold = T)%>%
  kable_styling(font_size = 7, latex_options = 'h')%>%
  column_spec(c(2,3), width = "19px") %>%
  column_spec(4, width = "40px") %>%
  column_spec(6, width = "36px") %>%
  column_spec(8, width = "72px") 
```

In order to observe the effectiveness of the model fit then, figures are drawn for comparing the predicted and observed values.

The 95% confidence interval of the prediction is shaded, and the wider the confidence interval, the wider the shaded part. Consequently, the width of the shaded portion in the plot of predicted versus observed values gives a clearer understanding of the uncertainty in the predicted results.

The fitted out regression line gives a straightforward way to describe the overall trend of the model and how well the model fits. This line is supposed to offer a good match to the data points in the scatter plot.

The figures of the Prob. of each explanatory variable using the fitted model show below:

```{r, echo = TRUE,eval = TRUE,  out.width = '70%', fig.align = "center", warning = FALSE,  fig.pos="H",fig.cap = '\\label{fig:rate} Comparing predictions and observations.'}
#get the plots of the Prob. of each explanatory variable using the fitted model
plot_model(model.film,type = "pred",
           title = "Prob. of the rate of the film greater than 7")
```

As can be seen in the three cases of continuous type variables (Figures 6-8), the shaded part of the picture is moderately wide and the fitting line falls within the shaded part, which demonstrates that this model is effective. Based on the figures we got, we can have a more detailed interpretation, for example:

The regression model of Budget vs. probability of film rating greater than 7 clearly shows that: 

- Within the range of 10, probability of film rating greater than 7 slightly increases as budget increases

- Within the range from 10 to 15, probability of film rating greater than 7 increasing rate rises a little bit

- Within the range greater 15, probability of film rating greater than 7 largely increases as budget increases

The regression model of Genre vs. probability of film rating greater than 7 clearly shows that:

- The films with genre: "Drama", "Action", "Animation" and "Romance" always have low probability of film rating greater than 7

- The films with genre: "Documentary", "Comedy" and "Short" always have high probability of film rating greater than 7

- However, genre "Short" film's probability fluctuates a lot.